Pillar 2- Quick Topic Models

### 2019-04-16 Pillar 2 - Tmp Topic Modeling.Rmd

###Functions for internal faceting
We create the functions for internal faceting taken from https://github.com/dgrtwo/drlib/blob/master/R/reorder_within.R
```{r function reorder_within & co., echo = FALSE, eval = TRUE}

@@

)
```
We create a helping control that we can use when we need fast convergence for testing new code. Thus, the control parameters we use for fast testing are:
```{r fast control}
my_control_fast <- list(

@@

##Plots - Model Evaluation
To evaluate how many topics are optimal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin){

@@

#Plot
plot_evaluation("catalogues")
plot_evaluation("manuals")
```
##Different alphas and delta (prior of term distributions over topics)
To evaluate the impact of the initial alpha and beta on our model, we train the model using different inizialization values for alpha and delta. Note that this is only an inizialisation and the algorithm will try to extimate alpha and beta.
###Alpha
```{r alpha and beta}
sample_dtm <- tb_topic_model$DTM[[1]] #1 CATALOGUES, 2 MANUALS

@@

         #Loglikelihood
         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik))
```
#Beta
```{r alpha and beta}

@@

##Saving model_data:
We save the data from our intermediate step in case further analysis is needed.
```{r save, eval = T}
#save(tb_topic_model, file = "Output/tb_topic_model.RDATA" )
```

#App
For our Recommender System, we need to pass the distributions, number of topics, origin, and key words to the app.
##Distributions and Key words
The function `clean_kw` removes stopwords from our key words.
```{r function clean key words}
clean_kw <- function(kw_list){

@@

```
On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
```{r crop and clean TM for App}
app_topic_model <- tb_topic_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
  mutate(kw = map(kw, .f = clean_kw))
```

##Convenience Vectors
For the app we also need to have a list of all courses and an example of a prospective semester
```{r for convenience}
# set seed
set.seed(1)

@@

```{r adding convenience vectors}
app_topic_model <- app_topic_model %>%
  mutate(`All Courses`     = list(course_all),
         `Sample semester` = list(course_following_semester))

#rm(course_all, course_following_semester)
```
## Saving files for APP
We save all requirements for the app.
```{r app files}
# save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
```

>>>>

```
###Preparation of course_title vector
```{r course titles, eval = TRUE}
#Clean titles
course_titles <-  d_text$catalogues %>%
  select(`Course ID`, `Course Title`, department) %>% 
  distinct

empty_titles <- course_titles %>% filter(`Course Title` == "")

```
###Functions for internal faceting
We create the functions for internal faceting taken from https://github.com/dgrtwo/drlib/blob/master/R/reorder_within.R
```{r function reorder_within & co., echo = FALSE, eval = TRUE}

@@

)
```
We create a helping control that we can use when we need fast convergence for testing new code. Thus, the control parameters we use for fast testing are:
```{r fast control, eval = TRUE}
my_control_fast <- list(

@@

##Plots - Model Evaluation
To evaluate how many topics are optimal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = FALSE}
#Function
plot_evaluation <- function(origin){

@@

#Plot
plot_evaluation("catalogues")
plot_evaluation("manuals")
```
##Different alphas and delta (prior of term distributions over topics)
To evaluate the impact of the initial alpha and beta on our model, we train the model using different inizialization values for alpha and delta. Note that this is only an inizialisation and the algorithm will try to extimate alpha and beta.
###Alpha
```{r alpha and beta, eval = FALSE}
sample_dtm <- tb_topic_model$DTM[[1]] #1 CATALOGUES, 2 MANUALS

@@

         #Loglikelihood
         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik))
```
#Beta
```{r alpha and beta, eval = FALSE}

@@

##Saving model_data:
We save the data from our intermediate step in case further analysis is needed.
```{r save, eval = TRUE}
#save(tb_topic_model, file = "Output/tb_topic_model.RDATA" )
```

#App
For our Recommender System, we need to pass the distributions, number of topics, origin, and key words to the app.
##Distributions and Key words
The function `clean_kw` removes stopwords from our key words.
```{r function clean key words, eval = T}
clean_kw <- function(kw_list){

@@

```
On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
```{r crop and clean TM for App, eval = T}
app_topic_model <- tb_topic_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
  mutate(kw = map(kw, .f = clean_kw))
```

##Convenience Vectors
For the app we also need to have a list of all courses and an example of a prospective semester
```{r for convenience, eval = T}
# set seed
set.seed(1)

@@

```{r adding convenience vectors, eval = T}
app_topic_model <- app_topic_model %>%
  mutate(`All Courses`     = list(course_all),
         `Sample semester` = list(course_following_semester),
         `Course Titles`   = list(course_titles) )

#rm(course_all, course_following_semester)
```
## Saving files for APP
We save all requirements for the app.
```{r app files, eval = T}
save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
```
